---
title: "Project Report : Predicting Win Probability in DoTA2 Using Logistic Regression"
author: "Paraskumar (1801035), Karthigeyan (1801093), Shanmugapriya (1801115), Raju (1801166), Niranjan (1801122)"
date: "06/08/2019"
output: word_document
---

```{r setup, include=FALSE}
dota2<-read.csv("dota2_final_v0.csv", colClasses = "factor")
dota2.hero<-dota2
dota2.hero$region<-NULL
library(pROC)
library(MASS)
library(ggplot2)
library(lattice)
library(caret)
library(pscl)
library(ResourceSelection)
library(DescTools)
knitr::opts_chunk$set(echo = TRUE)
```

### Introduction
The World Economic Forum projects eSports (Electronic Sports) industry to reach $1.4 billion by 2020. The growing popularity of eSports has also cought the attention of social media sites like YouTube and Twitch, which has recetly started live gaming streams to capture this market. One of the major eSports tounament covered is annual DoTA2 tournament "The International" with a total prize money worth around \$20 million in 2016. With this context we plan to build a logistic regression model to predict the probability of winnig a DoTA2 game given the hero selection by the teams.

DoTA2 is a popular MOBA (Multiplayer online battle arena) game. The gameplay consists of two teams with 5 players each. The games obejective is to select and control appropriate heros from a selection and defeat the other team. The heros chosen by the teams are mutually exclusive. For the present problem we use the data obtained from the UCI Machine learning repository. The data  was collected on the last day of the "The International" tournament held on the $13^{th}$ of August 2016 within a span of two hours using the API provided by the game developers.

### Data Structure
For our convenience we will use only the data corresponding to the game type as "Tournament" and game mode as "Captains Mode". This data is composed of 41,229 rows. Further we decoupled the hero selections for the two teams into two set of 111 each for each side. The cell value of 1 indicates that the hero is chosen while 0 indicates not choosing.
```{r}
head(dota2)
```




### Data Cleaning
The majority of the data cleaning ws carried out in Microsoft Excel. We had to decouple the hero selection and hence created a another set of 111 columns to display the enemies chosen by the other team. Also the region column had to be converted from integer to a string to increase readability.

### Data Understanding
 
```{r}
dota2<-read.csv("dota2_final_v0.csv", colClasses = "factor")
dota2.hero<-dota2
dota2.hero$region<-NULL
```

Here the first column tells whether the target team won (=1) or lost the match (=0). The region tell us the geographical server on which the game was played. The columns names with "choose_" before the hero name tells if the radiant team chose (=1) that particular hero or not (=0). The column names with "find_" before the hero name tells if the dire team chost (=1) that particular hero or not (=0). The entire dataset contains  

### Model
We made a logistic regression where we find how choosing a particular characters affects your probability of winning

#Logistic Regression Model

```{r}

```

# Exponential of Coefficients

```{r}

```