---
title: "Marriot Hotel Room Demand Forecasting"
author: "Business Forecasting Group 2 - Team 10 :Paraskumar, Karthigeyan, Shanmuga Priya, Raju, Niranjan a.k.a GOD"
date: "18/07/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data Cleaning
We First clean the data by converting the respective columns as factors and extract the data subset which will be used in the calculations.

```{r}
#### Data Cleaning
library(readxl)
marriot<-read_excel("Marriot_data (1).xlsx")
marriot$`DOW INDICATOR1`<-factor(marriot$`DOW INDICATOR1`)
DOW<-c("Saturday","Sunday","Monday","Tuesday","Wednesday","Thursday","Friday")
levels(marriot$`DOW INDICATOR1`)<-DOW
marriot$WEEK<-factor(marriot$WEEK)
levels(marriot$WEEK)<-c("Week 1","Week 2","Week 3","Week 4","Week 5","Week 6","Week 7",
                        "Week 8","Week 9","Week 10","Week 11","Week 12","Week 13","Week 14")
marriot[,c(7,8,9,10,11)]<-NULL
data.subset<-data.frame(Demand= marriot$DEMAND[1:87], Day = marriot$`DOW INDICATOR1`[1:87], Week = marriot$WEEK[1:87])
str(data.subset)

```

# Exploratory Data Anlysis

## Univariate Analysis
Here we find the descriptive statistics of the hotel room demand.

```{r}
##Univariate Analysis
summary(data.subset$Demand)
```

We are also interested in how the demand varies per day and per week. This is captured in the following plots.

```{r}
library(ggplot2)
demand.day<-ggplot(data.subset,aes(x = data.subset$Day ,
                                   y = data.subset$Demand,
                                   fill=data.subset$Day))+geom_boxplot()
demand.day+labs(title = "Demand Variation Across Weeks",
                x="Day of Week", y="No. Of Rooms Demanded", 
                fill="Days of the Week")+
                theme(axis.text.x = element_blank(), plot.title = element_text(hjust = 0.5))

demand.week<-ggplot(data.subset,aes(x = data.subset$Week,
                                    y = data.subset$Demand,
                                    fill=data.subset$Week))+geom_boxplot()
demand.week+labs(title = "Demand Variation Across Weeks",
                x="Week No.", y="No. Of Rooms Demanded", 
                fill="Week No.")+
                theme(axis.text.x = element_blank(),plot.title = element_text(hjust = 0.5))

```

## Time Series Plots

We would like to visually inspect how the demand changes. 

```{r}
### Creating a time-series object
library(ggplot2)
library(forecast)
demand.ts<-ts(data.subset$Demand,frequency = 7)
autoplot(demand.ts, ylab = "Total no. of rooms demamded", xlab = "Week no.",
         main ="Marriot Hotel Rooms Demanded : May 23 - Aug 18,1987 " )+
         theme(plot.title = element_text(hjust = 0.5))

ggsubseriesplot(demand.ts) +
  ylab("No. Rooms Demanded") +
  ggtitle("Hotel Room Demand Variation")+theme(plot.title = element_text(hjust = 0.5))

ggseasonplot(demand.ts, year.labels=TRUE, year.labels.left=TRUE) +  ylab("No. of rooms demanded") +
  ggtitle("Seasonal plot: Room Demand variation")+theme(plot.title = element_text(hjust = 0.5))

```

Here we don't notice a trend but a seasonality. To further confirm we conduct the unit root test to identify if there are any random walks present.

#Forcasting Procedure

## Stationarity Check

```{r}
##Staionarity Tests
library(fUnitRoots)
adfTest(demand.ts) #  #p-value> 0.05 : Fail to reject null hypothesis = Non-stationarity
library(tseries)
kpss.test(demand.ts) #p-value> 0.05 : Fail to reject null hypothesis = Stationarity
```

The contradictory results from the above test further leads us to consider not just ARIMA models but also determinsitic trend-seasonality models.


## Model Building

### Naive
The simplest model to be considered is the naive forcast.
```{r}
#Naive
model.naive<-naive(demand.ts)
model.naive
checkresiduals(model.naive$residuals)
```


### ETS
Next, we consider the Holt-winter model.
```{r}
##Trend-Seasonality Decompositions
model.ets<-ets(demand.ts)
model.ets
plot(model.ets)
checkresiduals(model.ets$residuals)
model.ets$aic
accuracy(model.ets)
```

### ARIMA
Here, we consider ARIMA models.
```{r}
#Auto-ARIMA
model.arima<-auto.arima(demand.ts)
model.arima
checkresiduals(model.arima$residuals)
model.arima$aic
```


## Model Evaluation

Here we plot our models.

```{r}
library(ggplot2)
autoplot(demand.ts) +
  autolayer(fitted(model.ets), series = "ETS") +
  autolayer(fitted(model.arima), series = "Auto-ARIMA") +
  autolayer(fitted(model.naive), series = "Naive")+
  guides(colour = guide_legend(title = " "))
```


Now we compare the model AIC values and the MAPE for the three models.

```{r}
accuracy(model.naive)
accuracy(model.arima)
accuracy(model.ets)
```

By looking at the MAPE values we find the Holt-Winter model to give the best prediction.

# Forecast Reccomendation 

The last row of the output give the best estimate for Saturday (22 August 1987), the start of week 14. 

```{r}
m2<-forecast(model.ets, h=5);m2
```

# Suggestions To Improve Forecasting

We can further imporve the forecasting by considering a longer time interval. 


