---
title: "Variable Selection Methods"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
house <- read_excel("Housing.xlsx")
```

# Introduction
Here is the structure of house dataset
```{r, }
str(house)
```


# Variable Selection Methods

**Occam's razor** : All else being equal,the simplest explanation is the best one

Let k is the number of variables in the model and p=k+1 be the total number of parameters.

Best fit of regression model is trade of between explanation and parameters. The criteria for best fits

- Adjusted $R^2$: $1 - \frac{(1-R^2)(n-1)}{n-p}$
- AIC (Akaike's An Information Criterion) :  $2p +n(1+\ln(2\pi))+n\ln(SSE/n)$ (some software use this formula  $2p +n\ln(SSE/n)$ )
- BIC (Bayesian information criterion): $\ln(n)*p +n*(1+\ln(2*\pi))+n*\ln(SSE/n)$ 
- Mallows's Cp :  $\frac{SSE_p}{MSE_{fullmodel}} +2p-n$

```{r}
## Examples
m1 <- lm(data=house,log(price)~ log(lotsize))
AIC(m1) ## 250.7114
BIC(m1) ## 263.6193

```


## Choose a model by AIC in a Stepwise Algorithm 
### Forward Selection



```{r}
#Constant Model

house$logprice <- log(house$price)
house$loglotsize <- log(house$lotsize)

const_m <- lm(data=house, logprice~1)

#formula(lm(data=house, logprice~.))
full_model_eqn <- "logprice ~ loglotsize + bedrooms + bathrms + stories + driveway + 
    recroom + fullbase + gashw + airco + garagepl + prefarea "
full_m <- lm(data=house, full_model_eqn)

step(const_m, scope=list(lower=const_m, upper=full_m), direction="forward")

# lm(formula = price ~ loglotsize + bathrms + airco + prefarea + 
#     stories + garagepl + fullbase + gashw + driveway + recroom + 
#     bedrooms, data = house)

```

### Backward Selection


```{r}

step(full_m, direction="backward")


# lm(formula = logprice ~ loglotsize + bedrooms + bathrms + stories + 
#     driveway + recroom + fullbase + gashw + airco + garagepl + 
#     prefarea, data = house)

```
### Stepwise Selection


```{r}

step(const_m, scope=list(upper=full_m), direction="both")

# lm(formula = price ~ loglotsize + bathrms + airco + prefarea + 
#     stories + garagepl + fullbase + gashw + driveway + recroom + 
#     bedrooms, data = house)

```


## Best subset regression

This would require *leaps* package.

```{r}
library(leaps)
## This model is just an example; you could use 'price~.'
leaps=regsubsets(data=house,  logprice ~ loglotsize + bathrms + airco + stories + prefarea +  driveway, nbest=1)

plot(leaps,scale="adjr2")

```

